---
title: "Results Financial Inclusion"
author: "Juan C. Correa"
date: "22/11/2020"
output: pdf_document
---

```{r setup}
setwd("/home/juan/Documents/GitHub/Fin-Tech")
```
Let's open the data
```{r}
library(readr)
Brandstat <- read_delim("RawDataBrandstat.csv", ",", escape_double = FALSE, trim_ws = TRUE)
variable.names(Brandstat)
automation <- Brandstat[14:20]
TechDisp <- Brandstat[10:13]
```

# Sample Description
```{r}
library(psych)
describe.by(Brandstat$Age, group = Brandstat$Sex, mat = TRUE, digits = 2)
summary(Brandstat$Age)
library(ggplot2)
library(ggridges)
s1 <- ggplot(Brandstat, aes(x=Age, y=as.factor(Sex))) + geom_density_ridges(fill="green", alpha = 0.4) + 
theme_ridges() + ylab("Sex")

s2 <- ggplot(Brandstat, aes(x=Age, y=as.factor(Strata))) + geom_density_ridges(fill="green", alpha = 0.4) + 
theme_ridges() + ylab("Economic Strata")

s3 <- ggplot(Brandstat, aes(x=Age, y=as.factor(Education))) + geom_density_ridges(fill="green", alpha = 0.4)+ 
theme_ridges() + ylab("Education")

s4 <- ggplot(Brandstat, aes(x=Age, y=as.factor(Home_Structure))) + geom_density_ridges(fill="green", alpha = 0.4)+ 
theme_ridges() + ylab("Home Structure")

library(ggpubr)

ggarrange(s1, s2, s3, s4, ncol = 2, nrow = 2, labels = c("    A","    B","    C","    D"))


```


# Measurement Model of Automation

To examine the factor structure of all the scales employed, we proceed by testing the overall sampling adequacy of the items. These items are susceptible to factorization (KMO = 0.92), and the most probable psychometric structure consists of a one-factor model with freely estimated factor loadings. This emerging solution is evident through the statistical significance of the homogeneous items test (F = 1.763; p = 0.0415) which proved to be better than a psychometric structure of a one-factor model with equal factor loadings for all items captured by the tau-equivalence test (F = 1.563; p = 0.0575).
```{r}
library(psych)
KMO(automation)
library(coefficientalpha)
tau.test(automation)
```

The results of the confirmatory factor analysis reveal a reasonable goodness-of-fit for the scale of automation (CFI = 0.950; TLI = 0.926; RMSEA = 0.142; SRMR = 0.037)
```{r}
library(lavaan)
aut.model <- "aut =~ Aut1 + Aut2 + Aut3 + Aut4 + Aut5 + Aut6 + Aut7"
fit1 <- lavaan::cfa(aut.model, data=Brandstat,std.lv=TRUE)
summary(fit1, fit.measures=T,standardized=T)
library(semTools)
reliability(fit1)
```

The emerging psychometric structure is depicted in the following picture. 
```{r}
library(semPlot)
semPaths(fit1, whatLabels = "stand", layout = "tree", color = list(
              lat = rgb(255, 100, 118, maxColorValue = 255), 
              man = rgb(155, 253, 175, maxColorValue = 255)),
          mar = c(10, 5, 10, 5), intercepts = FALSE, residuls = FALSE, nCharNodes = 0)
```


# Measurement Model of Technology Disposition
The items of the scale of Technology Disposition are also susceptible to factorization (KMO = 0.67), and the most probable psychometric structure consists of a one-factor model.

```{r}
library(psych)
KMO(TechDisp)
library(coefficientalpha)
tau.test(TechDisp)
```


The Measurement model of technology disposition reveals also a reasonable goodness-of-fit, as can be seen in the following results (CFI = 0.996; TLI = 0.987; RMSEA = 0.034; SRMR = 0.018)
```{r}
library(lavaan)
TD.model <- "TD =~ TD1 + TD2 + TD3 + TD4"
fit2 <- lavaan::cfa(TD.model, data=Brandstat,std.lv=TRUE)
summary(fit2, fit.measures=T,standardized=T)
inspect(fit2, "rsquare")
library(semTools)
reliability(fit2)
```

The emerging psychometric structure is depicted in the following picture. 
```{r}
library(semPlot)
semPaths(fit2, whatLabels = "stand", layout = "tree", color = list(
              lat = rgb(255, 100, 118, maxColorValue = 255), 
              man = rgb(155, 253, 175, maxColorValue = 255)),
          mar = c(10, 5, 10, 5), intercepts = FALSE, residuls = FALSE, nCharNodes = 0)
```


# Structural Model: Technology Disposition as Predictor of Automation

Our structural model posits that technology disposition predicts the acceptance of technology through the automation of financial processes. This set of relationships are summarized and illustrated as follows

```{r}
library(lavaan);
modelData <- Brandstat
 model<-"
! regressions 
   Automation=~Aut__Aut1*Aut1
   Automation=~Aut__Aut2*Aut2
   Automation=~Aut__Aut3*Aut3
   Automation=~Aut__Aut4*Aut4
   Automation=~Aut__Aut5*Aut5
   Automation=~Aut__Aut6*Aut6
   Automation=~Aut__Aut7*Aut7
   TD=~TD__TD1*TD1
   TD=~TD__TD4*TD4
   TD=~TD__TD2*TD2
   TD=~TD__TD3*TD3
   TD=~TD__Automation*Automation
! residuals, variances and covariances
   Automation ~~ 1.0*Automation
   Aut1 ~~ VAR_Aut1*Aut1
   Aut2 ~~ VAR_Aut2*Aut2
   Aut3 ~~ VAR_Aut3*Aut3
   Aut4 ~~ VAR_Aut4*Aut4
   Aut5 ~~ VAR_Aut5*Aut5
   Aut6 ~~ VAR_Aut6*Aut6
   Aut7 ~~ VAR_Aut7*Aut7
   TD ~~ 1.0*TD
   TD1 ~~ VAR_TD1*TD1
   TD4 ~~ VAR_TD4*TD4
   TD2 ~~ VAR_TD2*TD2
   TD3 ~~ VAR_TD3*TD3
! observed means
   Aut1~1;
   Aut2~1;
   Aut3~1;
   Aut4~1;
   Aut5~1;
   Aut6~1;
   Aut7~1;
   TD1~1;
   TD4~1;
   TD2~1;
   TD3~1;
";
result<- sem(model, data=modelData);
summary(result, fit.measures=TRUE);
standardizedSolution(result)
inspect(result, "rsquare")
```


```{r}
library(semPlot)
semPaths(result, whatLabels = "std", layout = "spring", color = list(
              lat = rgb(255, 100, 118, maxColorValue = 255), 
              man = rgb(155, 253, 175, maxColorValue = 255)),
          mar = c(10, 5, 10, 5), intercepts = FALSE, residuls = FALSE, nCharNodes = 0)
```
